### 2021-05-18 chatbot_classification/03.emnlp_2021/appendix.tex
modified:   abstract.tex   modified:   appendix.tex   modified:   experiments.tex   modified:   introduction.tex   modified:   open.sh   modified:   paper.tex

@@

\newpage
\section{Appendix}

\subsection{Related work}
We supplement some work that is very different from classic classification models.

@@

\subsection{Settings  of  hyperparameters} 
In  Table \ref{tbe:table3}, we explore the influence from hyperparameters, which
are  the  number  of  candidate  class  labels $K$ in stage 1, and the number of
sampled  sentence  pairs  for  each class $P$ in stage 2, on ITG and Amazon-670K
datasets.  As we control the total number of sampled sentence pairs to about 50 to 60, we
roughly obatin five combinations of hyperparameters.

We find  that the best setting of hyperparameters is different from datasets
of  different  data  size.  The  class label number of ITG and Amazon-670k are
similar  in  our  experimental setting, which is around 250. However the total
amount of data points of ITG is approximately 2 times larger than Amazon-670k.
Therefore,  the  setting of $K=5$ and $P=10$ is good enough for ITG since most
of  the  classes  contains  over 10 data points. However, for Amazon-670k, the
amount  of  data  sample  for  each  class  is  scarce, thus, we may need more
candidate  classes to sample enough effective sentence pairs for sentence-pair
model  layer  of  SFC.  In this way, the setting of $K=10$ and $P=5$ becomes a
good choice.

However,  in  spite of the effect on evaluation performance brought by different
settings  of hyperparameters, joint-SFC still steadily outperforms two-stage SFC
by  0.41  percent  points  in  overall  average  F1 score on ITG and Amazon-670k
datasets.

>>>>

\newpage

@@

\section{Appendix}
\subsection{Related work}
We supplement some work that is very different from classic classification models.

@@

### 2021-05-18 chatbot_classification/03.emnlp_2021/experiments.tex
modified:   abstract.tex   modified:   appendix.tex   modified:   experiments.tex   modified:   introduction.tex   modified:   open.sh   modified:   paper.tex

>>>>

\subsection{Settings  of  hyperparameters} 
In  Table \ref{tbe:table3}, we explore the influence from hyperparameters, which
are  the  number  of  candidate  class  labels $K$ in stage 1, and the number of
sampled  sentence  pairs  for  each class $P$ in stage 2, on ITG and Amazon-670K
datasets.  As we control the total number of sampled sentence pairs to about 50 to 60, we
roughly obatin five combinations of hyperparameters.

We find  that the best setting of hyperparameters is different from datasets
of  different  data  size.  The  class label number of ITG and Amazon-670k are
similar  in  our  experimental setting, which is around 250. However the total
amount of data points of ITG is approximately 2 times larger than Amazon-670k.
Therefore,  the  setting of $K=5$ and $P=10$ is good enough for ITG since most
of  the  classes  contains  over 10 data points. However, for Amazon-670k, the
amount  of  data  sample  for  each  class  is  scarce, thus, we may need more
candidate  classes to sample enough effective sentence pairs for sentence-pair
model  layer  of  SFC.  In this way, the setting of $K=10$ and $P=5$ becomes a
good choice.

However,  in  spite of the effect on evaluation performance brought by different
settings  of hyperparameters, joint-SFC still steadily outperforms two-stage SFC
by  0.41  percent  points  in  overall  average  F1 score on ITG and Amazon-670k
datasets.

### 2021-05-18 chatbot_classification/03.emnlp_2021/introduction.tex
modified:   introduction.tex
modified:   abstract.tex   modified:   appendix.tex   modified:   experiments.tex   modified:   introduction.tex   modified:   open.sh   modified:   paper.tex

Experiment  results  from  6  public  and  1  private  short-text classification datasets,  show  that  our proposed SFC joint system can achieve significant and consistent  improvements  over  strong baselines, especially in the low resource settings.

\begin{figure*}[t]
  \begin{centering}
    \includegraphics[scale=0.66]{picture/picture4} 
    \par
  \end{centering}
  \caption{
    \textbf{Network Structure of SFC:} 2-stage SFC and joint-SFC are sharing
    the  same  network  from  stage  1  and  stage 2, with the only difference
    whether two stages being jointly trained.
  }
  \label{fig:framework}
\end{figure*}

>>>>

\begin{figure*}[t]
  \begin{centering}
    \includegraphics[scale=0.66]{picture/picture4} 
    \par
  \end{centering}
  \caption{
    \textbf{Network Structure of SFC:} 2-stage SFC and joint-SFC are sharing the same network, with the only difference whether the two stages being jointly trained.
  }
  \label{fig:framework}
\end{figure*}
